### 2022-11-12 index.Rmd
first commit

---
title: Quality control for the target decoy approach for peptide identification
output:
    html_document:
      code_download: false
      toc: false
      toc_float: false
      number_sections: false

---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

***

This repo contains all necessary files to perform all data analyses and generate all figures for our paper: "Quality control for the target decoy approach for peptide identification"

Generate all figures: [paper_figures](./paper_figures.html)
Document with supplementary figures: [supplementary_figures](./paper_supplementary.pdf)

### 2022-11-12 paper_supplementary.Rmd
first commit

---
title: "Supplementary Figures: Quality control for the target decoy approach for peptide identification"
author: 
  Elke Debrie$^1$
  Milan Malfait$^1$
  Ralf Gabriels$^{2,3}$
  Arthur Declerq$^{2,3}$
  Adriaan Sticker$^{2,3}$
  Lennart Martens$^{2,3}$
  Lieven Clement$^{1,4}$
date: 
  $^1$ Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent, Belgium \newline
  $^2$ VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium \newline
  $^3$ Department of Biomolecular Medicine, Ghent University, Ghent, Belgium \newline
  $^4$ Corresponding Author$:$ lieven.clement@ugent.be
output: 
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: xelatex
    citation_package: natbib
    toc: no
link-citations: yes
bibliography: [biblio.bib]
biblio-style: biochem
linkcolor: blue
urlcolor: blue
citecolor: blue
---

\setcitestyle{super,open={[},close={]}}
\def\citenumfont{}

(ref:Figure1)  Histogram and PP-plot for a concatenated search on a *Pyrococcus* run against a database of canonical *P. furiosus* sequences from Swiss-Prot using X!Tandem without refinement. Both the histogram and the P-P plot show no violation of the TDA assumptions.

```{r sFig1, echo=FALSE, fig.cap="(ref:Figure1)",out.width="99%"}
knitr::include_graphics("./figs/figTandemNoRefineSwissHistPP.png")
```

(ref:Figure2)  Histogram and PP-plot for a concatenated search on a *H. sapiens* run against a database of *H. Sapiens* sequences from UniProt using MS-GF+. Both the histogram and the P-P plot show no violation of the TDA assumptions.

```{r sFig2, echo=FALSE, fig.cap="(ref:Figure2)",out.width="99%"}
knitr::include_graphics("./figs/figHumanMsgfPlus.png")
```

(ref:Figure3)  Histogram and PP-plot for a concatenated search on an immunopeptidomics run using Andromeda. Both the histogram and the P-P plot show no violation of the TDA assumptions.

```{r sFig3, echo=FALSE, fig.cap="(ref:Figure3)",out.width="99%"}
knitr::include_graphics("./figs/figPeptidomics.png")
```

(ref:Figure4)  Histogram and PP-plot for rank 2 target and decoy PSM scores of a concatenated search on a H. sapiens run against a database of H. Sapiens sequences from UniProt using MS-GF+.

```{r sFig4, echo=FALSE, fig.cap="(ref:Figure4)",out.width="99%"}
knitr::include_graphics("./figs/figHumanMsgfPlusR2.png")
```

### 2022-11-13 paper_supplementary.tex
Deploying to gh-pages from  @ abd0311b29775e7e99b545b28d9f7e4e6b8a00c7 🚀

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{biochem}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary Figures: Quality control for the target decoy approach for peptide identification},
  pdfauthor={Elke Debrie\^{}1 Milan Malfait\^{}1 Ralf Gabriels\^{}\{2,3\} Arthur Declerq\^{}\{2,3\} Adriaan Sticker\^{}\{2,3\} Lennart Martens\^{}\{2,3\} Lieven Clement\^{}\{1,4\}},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary Figures: Quality control for the target decoy approach for peptide identification}
\author{Elke Debrie\(^1\) Milan Malfait\(^1\) Ralf Gabriels\(^{2,3}\) Arthur Declerq\(^{2,3}\) Adriaan Sticker\(^{2,3}\) Lennart Martens\(^{2,3}\) Lieven Clement\(^{1,4}\)}
\date{\(^1\) Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent, Belgium \newline \(^2\) VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium \newline \(^3\) Department of Biomolecular Medicine, Ghent University, Ghent, Belgium \newline \(^4\) Corresponding Author\(:\) \href{mailto:lieven.clement@ugent.be}{\nolinkurl{lieven.clement@ugent.be}}}

\begin{document}
\maketitle

\setcitestyle{super,open={[},close={]}}
\def\citenumfont{}

\begin{figure}
\includegraphics[width=0.99\linewidth]{./figs/figTandemNoRefineSwissHistPP} \caption{Histogram and PP-plot for a concatenated search on a \emph{Pyrococcus} run against a database of canonical \emph{P. furiosus} sequences from Swiss-Prot using X!Tandem without refinement. Both the histogram and the P-P plot show no violation of the TDA assumptions.}\label{fig:sFig1}
\end{figure}

\begin{figure}
\includegraphics[width=0.99\linewidth]{./figs/figHumanMsgfPlus} \caption{Histogram and PP-plot for a concatenated search on a \emph{H. sapiens} run against a database of \emph{H. Sapiens} sequences from UniProt using MS-GF+. Both the histogram and the P-P plot show no violation of the TDA assumptions.}\label{fig:sFig2}
\end{figure}

\begin{figure}
\includegraphics[width=0.99\linewidth]{./figs/figPeptidomics} \caption{Histogram and PP-plot for a concatenated search on an immunopeptidomics run using Andromeda. Both the histogram and the P-P plot show no violation of the TDA assumptions.}\label{fig:sFig3}
\end{figure}

\begin{figure}
\includegraphics[width=0.99\linewidth]{./figs/figHumanMsgfPlusR2} \caption{Histogram and PP-plot for rank 2 target and decoy PSM scores of a concatenated search on a H. sapiens run against a database of H. Sapiens sequences from UniProt using MS-GF+.}\label{fig:sFig4}
\end{figure}

  \bibliography{biblio.bib}

\end{document}

### 2022-11-13 paper_supplementary.Rmd
comply with achemso template of JPR + add myTemplate.tex

@@
 title: "Supplementary Figures: Quality control for the target decoy approach for peptide identification"
-author: 
-  Elke Debrie$^1$
-  Milan Malfait$^1$
-  Ralf Gabriels$^{2,3}$
-  Arthur Declerq$^{2,3}$
-  Adriaan Sticker$^{2,3}$
-  Lennart Martens$^{2,3}$
-  Lieven Clement$^{1,4}$
-date: 
-  $^1$ Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent, Belgium \newline
-  $^2$ VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium \newline
-  $^3$ Department of Biomolecular Medicine, Ghent University, Ghent, Belgium \newline
-  $^4$ Corresponding Author$:$ lieven.clement@ugent.be
 output: 
   bookdown::pdf_document2:
+    template: "myTemp.tex"
     keep_tex: yes
     latex_engine: xelatex
+    toc: no
     citation_package: natbib
-    toc: no
-link-citations: yes
+    includes:
+      in_header: authors.tex
+
+documentclass: achemso
+classoption: 
+  - journal=jprobs
+  - manuscript=article
+
 bibliography: [biblio.bib]
-biblio-style: biochem
 linkcolor: blue
@@
 
-\setcitestyle{super,open={[},close={]}}
-\def\citenumfont{}
+```{r echo=FALSE, warning=FALSE}
+if (!tinytex::check_installed("achemso")) tinytex::tlmgr_install("achemso")
+if (!tinytex::check_installed("caption")) tinytex::tlmgr_install("caption")
+if (!tinytex::check_installed("setspace")) tinytex::tlmgr_install("setspace")
+```
 

### 2022-11-13 index.Rmd
update index.Rmd

@@
 
-This repo contains all necessary files to perform all data analyses and generate all figures for our paper: "Quality control for the target decoy approach for peptide identification"
+This repository contains all necessary files to perform all data analyses and generate all figures for our paper: "Quality control for the target decoy approach for peptide identification"
 
-Generate all figures: [paper_figures](./paper_figures.html)
-Document with supplementary figures: [supplementary_figures](./paper_supplementary.pdf)
+- Generate all Figures: [paper_figures](./paper_figures.html)
+
+- Document with Supplementary Figures: [supplementary_figures](./paper_supplementary.pdf)

### 2022-11-13 authors.tex
Deploying to gh-pages from  @ cc10a4a1fd0243cdda341bab08a8ed48ef11c95f 🚀

\author{Elke Debrie}
\affiliation[Ghent University]
{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}

\author{Milan Malfait}
\affiliation[Ghent University]
{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}

\author{Ralf Gabriels}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Arthur Declerq}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Adriaan Sticker}
\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\alsoaffiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Lennart Martens}
\affiliation[VIB-UGent]
{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
\alsoaffiliation[Ghent University]
{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}

\author{Lieven Clement}
\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
\email{lieven.clement@ugent.be}

### 2022-11-13 paper_supplementary.tex
Deploying to gh-pages from  @ cc10a4a1fd0243cdda341bab08a8ed48ef11c95f 🚀

@@
 % Options for packages loaded elsewhere
+% Motified template from 
+% https://github.com/jgm/pandoc/blob/master/data/templates/default.latex
+% Removed author
+% Removed natbib
+% to comply with achemso document class
+% authors in author.tex via includes: in_header:
 \PassOptionsToPackage{unicode}{hyperref}
@@
 \documentclass[
-]{article}
+  journal=jprobs,
+  manuscript=article]{achemso}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
 \usepackage{longtable,booktabs,array}
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
+
+\author{Elke Debrie}
+\affiliation[Ghent University]
+{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
+
+\author{Milan Malfait}
+\affiliation[Ghent University]
+{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
+
+\author{Ralf Gabriels}
+\affiliation[VIB-UGent]
+{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
+\alsoaffiliation[Ghent University]
+{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
+
+\author{Arthur Declerq}
+\affiliation[VIB-UGent]
+{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
+\alsoaffiliation[Ghent University]
+{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
+
+\author{Adriaan Sticker}
+\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
+\alsoaffiliation[VIB-UGent]
+{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
+\alsoaffiliation[Ghent University]
+{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
+
+\author{Lennart Martens}
+\affiliation[VIB-UGent]
+{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
+\alsoaffiliation[Ghent University]
+{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
+
+\author{Lieven Clement}
+\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
+\email{lieven.clement@ugent.be}
 \ifLuaTeX
@@
 \fi
-\usepackage[]{natbib}
-\bibliographystyle{biochem}
+%natbib deleted from template
+
 \IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
@@
   pdftitle={Supplementary Figures: Quality control for the target decoy approach for peptide identification},
-  pdfauthor={Elke Debrie\^{}1 Milan Malfait\^{}1 Ralf Gabriels\^{}\{2,3\} Arthur Declerq\^{}\{2,3\} Adriaan Sticker\^{}\{2,3\} Lennart Martens\^{}\{2,3\} Lieven Clement\^{}\{1,4\}},
   colorlinks=true,
@@
 \title{Supplementary Figures: Quality control for the target decoy approach for peptide identification}
-\author{Elke Debrie\(^1\) Milan Malfait\(^1\) Ralf Gabriels\(^{2,3}\) Arthur Declerq\(^{2,3}\) Adriaan Sticker\(^{2,3}\) Lennart Martens\(^{2,3}\) Lieven Clement\(^{1,4}\)}
-\date{\(^1\) Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent, Belgium \newline \(^2\) VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium \newline \(^3\) Department of Biomolecular Medicine, Ghent University, Ghent, Belgium \newline \(^4\) Corresponding Author\(:\) \href{mailto:lieven.clement@ugent.be}{\nolinkurl{lieven.clement@ugent.be}}}
+% remove author
+\date{}
 
@@
 
-\setcitestyle{super,open={[},close={]}}
-\def\citenumfont{}
+\begin{verbatim}
+## tlmgr install achemso
+\end{verbatim}
+
+\begin{verbatim}
+## tlmgr install caption
+\end{verbatim}
+
+\begin{verbatim}
+## tlmgr install setspace
+\end{verbatim}
 

### 2022-11-13 index.Rmd
update theme index.html

@@
       number_sections: false
-
+      theme: flatly
+      highlight: tango
 ---

### 2022-11-14 paper_supplementary.Rmd
update figures.Rmd with graphical abstract

@@
 
-```{r echo=FALSE, warning=FALSE}
+```{r echo=FALSE, warning=FALSE, message=FALSE}
 if (!tinytex::check_installed("achemso")) tinytex::tlmgr_install("achemso")

### 2022-11-17 authors.tex
update paper_figures with tiff files

@@
 {Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
+\alsoaffiliation[Janssen]{Statistics and Decision Sciences, Janssen Pharmaceutical Companies of Johnson and Johnson, Beerse, Belgium}
 
@@
 \affiliation[VIB-UGent]
-{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
+{VIB-UGent Center for Medical Biotechnology, VIB, Ghent, Belgium}
 \alsoaffiliation[Ghent University]
@@
 \alsoaffiliation[VIB-UGent]
-{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
+{VIB-UGent Center for Medical Biotechnology, VIB, Ghent, Belgium}
 \alsoaffiliation[Ghent University]

### 2022-11-17 supplementaryBackMatter.tex
update paper_figures with tiff files

--- 2022-11-13 paper_supplementary.tex
@@
-% Options for packages loaded elsewhere
-% Motified template from 
-% https://github.com/jgm/pandoc/blob/master/data/templates/default.latex
-% Removed author
-% Removed natbib
-% to comply with achemso document class
-% authors in author.tex via includes: in_header:
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
-%
-\documentclass[
-  journal=jprobs,
-  manuscript=article]{achemso}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
+\newpage
 
-\author{Elke Debrie}
-\affiliation[Ghent University]
-{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
+\section{Supplementary Figures}
 
-\author{Milan Malfait}
-\affiliation[Ghent University]
-{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
-
-\author{Ralf Gabriels}
-\affiliation[VIB-UGent]
-{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
-\alsoaffiliation[Ghent University]
-{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
-
-\author{Arthur Declerq}
-\affiliation[VIB-UGent]
-{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
-\alsoaffiliation[Ghent University]
-{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
-
-\author{Adriaan Sticker}
-\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
-\alsoaffiliation[VIB-UGent]
-{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
-\alsoaffiliation[Ghent University]
-{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
-
-\author{Lennart Martens}
-\affiliation[VIB-UGent]
-{VIB-UGent Center for Medical Biotechnology, VIB, Zwijnaarde, Belgium}
-\alsoaffiliation[Ghent University]
-{Department of Biomolecular Medicine, Ghent University, Ghent, Belgium}
-
-\author{Lieven Clement}
-\affiliation[Ghent University]{Department of Applied Mathematics, Computer Science and Statistics, Ghent University, Ghent University, Ghent, Belgium}
-\email{lieven.clement@ugent.be}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-%natbib deleted from template
-
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Supplementary Figures: Quality control for the target decoy approach for peptide identification},
-  colorlinks=true,
-  linkcolor={blue},
-  filecolor={Maroon},
-  citecolor={blue},
-  urlcolor={blue},
-  pdfcreator={LaTeX via pandoc}}
-
-\title{Supplementary Figures: Quality control for the target decoy approach for peptide identification}
-% remove author
-\date{}
-
-\begin{document}
-\maketitle
-
-\begin{verbatim}
-## tlmgr install achemso
-\end{verbatim}
-
-\begin{verbatim}
-## tlmgr install caption
-\end{verbatim}
-
-\begin{verbatim}
-## tlmgr install setspace
-\end{verbatim}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\setcounter{figure}{0}
+\renewcommand{\figurename}{Supplementary Figure}
 
@@
 \end{figure}
-
-  \bibliography{biblio.bib}
-
-\end{document}

### 2022-11-17 paper_supplementary.tex
Deploying to gh-pages from  @ 0ff2e0b7585c679da87a5a357bf75184df9d2f85 🚀
Deploying to gh-pages from  @ b38968b51bf33e5979228f9801ab203b1cb1e32b 🚀

@@
 
-\begin{verbatim}
-## tlmgr install achemso
-\end{verbatim}
-
-\begin{verbatim}
-## tlmgr install caption
-\end{verbatim}
-
-\begin{verbatim}
-## tlmgr install setspace
-\end{verbatim}
-
 \begin{figure}
